Same as always: I suck at titles

### 2024-09-13 manuscript/manuscript_eb.Rmd
first draft
sent to rob and martin

keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
wordcount         : "X"

@@

However, certain speech qualities can yield negative evaluations without being explicitly associated with those. One consistent finding is that speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., [@dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010]. This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014]. Alternatively, but not exclusively, it is possible that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018]. This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], why a statement is believed to be underinformative [@fairchildpapafragou2018; @fairchildetal2020; @lorenzonietal2022; @ippapafragou2022] and why non-native speech is processed shallower [@levarikeysar2012; @hanulikovetal2012].

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived [@jiangetal2019; @caballeropell2020]. Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listenes [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

>>>>

keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
wordcount         : "4774"

@@

Interestingly, who produces the information can also affect how it is evaluated. On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., [@dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021]. This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].

Alternatively, but not exclusively, speaker identity in itself can bias interpretation. Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret. @fairchildetal2020 asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story. Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this 'forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4). One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018]. This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], why a statement is believed to be underinformative [@fairchildpapafragou2018; @lorenzonietal2022; @ippapafragou2022] and why non-native speech is processed shallower [@levarikeysar2012; @hanulikovetal2012].

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is expected to be delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived [@jiangetal2019; @caballeropell2020]. Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listeners [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

### 2024-09-13 manuscript/manuscript_eb.tex
first draft
sent to rob and martin

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: X}
\usepackage{lineno}

@@

However, certain speech qualities can yield negative evaluations without being explicitly associated with those. One consistent finding is that speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., (Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Lev-Ari \& Keysar, 2010). This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013). Alternatively, but not exclusively, it is possible that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015). This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018), why a statement is believed to be underinformative (Fairchild, Mathis, \& Papafragou, 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022) and why non-native speech is processed shallower (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listenes (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

@@

After the betting round was complete, participants completed a questionnaire similar to that of Foucart, Costa, Morís-Fernández, and Hartsuiker (2020) to measure their language attitudes towards the native and the non-native speaker. For each speaker, participants answered six questions measuring affect (three questions for negative affect and three questions for positive affect), five questions measuring solidarity, five questions measuring status, and one question each for comprehensibility, accentedness, fluency, and trustworthiness. Each question used a 9-point scale. Participants first answered questions about, at random, the native or non-native speaker, with the order of presentation of dimensions being randomised. They then answered the same questions for the remaining speaker. We also asked participants to guess the countries of origin of our native and non-native speakers, and from which speaker they would like to learn about horse races in the future. Additional questions included ratings on a 9-point scale of how natural the audio sounded (1: unnatural, edited; 9: natural, unedited), and two questions measuring participants' exposure to native and non-native accented English (1: never; 9: always). Likewise, we measured participants' previous experience with betting and their perceived knowledge of horse races (two questions: Whether they had bet on horse races in the past, and to rate on a 5-point scale, from `Strongly disagree' to `Strongly agree', how closely they identified with the statement `I am an expert on horse races'). Finally, we included an open-ended question for participants to report what guided their decision-making, as well as their perception of the experiment's aim.

@@

@@

@@

@@

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 4774}
\usepackage{lineno}

@@

Interestingly, who produces the information can also affect how it is evaluated. On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., (Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021). This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013).

Alternatively, but not exclusively, speaker identity in itself can bias interpretation. Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret. Fairchild, Mathis, and Papafragou (2020) asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story. Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4). One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015). This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018), why a statement is believed to be underinformative (Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022) and why non-native speech is processed shallower (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is expected to be delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

@@

After the betting round was complete, participants completed a questionnaire similar to that of Foucart et al. (2020) to measure their language attitudes towards the native and the non-native speaker. For each speaker, participants answered six questions measuring affect (three questions for negative affect and three questions for positive affect), five questions measuring solidarity, five questions measuring status, and one question each for comprehensibility, accentedness, fluency, and trustworthiness. Each question used a 9-point scale. Participants first answered questions about, at random, the native or non-native speaker, with the order of presentation of dimensions being randomised. They then answered the same questions for the remaining speaker. We also asked participants to guess the countries of origin of our native and non-native speakers, and from which speaker they would like to learn about horse races in the future. Additional questions included ratings on a 9-point scale of how natural the audio sounded (1: unnatural, edited; 9: natural, unedited), and two questions measuring participants' exposure to native and non-native accented English (1: never; 9: always). Likewise, we measured participants' previous experience with betting and their perceived knowledge of horse races (two questions: Whether they had bet on horse races in the past, and to rate on a 5-point scale, from `Strongly disagree' to `Strongly agree', how closely they identified with the statement `I am an expert on horse races'). Finally, we included an open-ended question for participants to report what guided their decision-making, as well as their perception of the experiment's aim.

@@

\leavevmode\vadjust pre{\hypertarget{ref-barlowetal2024}{}}%
Barlow, S., Beardsley, G., Bsharah, Z., Crofts, R., De La Rosa, C., Gutierrez, A., et al.others. (2024). The effects of exposure and explicit stereotypes on veracity judgments of polish-accented english speech: A preregistered close replication and extension of boduch-grabka \& lev-ari (2021). \emph{Studies in Second Language Acquisition}, 1--17.

@@

\leavevmode\vadjust pre{\hypertarget{ref-foucarthartsuiker2021}{}}%
Foucart, A., \& Hartsuiker, R. J. (2021). Are foreign-accented speakers that {``incredible''}? The impact of the speaker's indexical properties on sentence processing. \emph{Neuropsychologia}, \emph{158}, 107902.

@@

\leavevmode\vadjust pre{\hypertarget{ref-souzamarkman2013}{}}%
Souza, A. L., \& Markman, A. B. (2013). Foreign accent does not influence cognitive judgments. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{35}.

\leavevmode\vadjust pre{\hypertarget{ref-stocker2017}{}}%
Stocker, L. (2017). The impact of foreign accent on credibility: An analysis of cognitive statement ratings in a swiss context. \emph{Journal of Psycholinguistic Research}, \emph{46}, 617--628.

@@

\leavevmode\vadjust pre{\hypertarget{ref-wetzeletal2021}{}}%
Wetzel, M., Zufferey, S., \& Gygax, P. (2021). Do non-native and unfamiliar accents sound less credible? An examination of the processing fluency hypothesis. \emph{Journal of Articles in Support of the Null Hypothesis}, \emph{17}(2).
